Manuscript

### 2019-12-27 manuscript.Rmd

@@

## Computational

**12/4 EDIT THIS**
```{r, include=FALSE}
r_v <- paste0("v", getRversion())
# rstudio_v <- paste0("v", RStudio.Version()$version)
ggplot_v <- paste0("v", packageVersion("ggplot2"))
ggpubr_v <- paste0("v", packageVersion("ggpubr"))
```

For *Figure 1*, all data were imported and manipulated using pandas (v0.23.0) [@mckinney2011] and plotted using seaborn (v0.90) [@waskom2012], which sat on top of matplotlib (v2.2.2) [@hunter2007] and was executed on Python (v2.7.15) (Python Software Foundation, https://www.python.org/) in an IPython (v5.5.0) [@perez2007] kernel within a localhost Jupyter (v5.2.2) notebook [@kluyver2016]. All other analyses were conducted in R (`r r_v`) [@rdevelopmentcoreteam2010, https://www.R-project.org/] in an RStudio environment (v1.1.447) [@rstudio2012]. All other plots were drawn using the ggplot2 (`r ggplot_v`) R package [@wickham2016].

### Statistics

Wilcoxon tests were conducted using the `compare_means` function in the ggpubr (`r ggpubr_v`) R package [@kassambara2018]. `compare_means` does Benjamini-Hochberg p-value adjustment using the `p.adjust` function from the `stats` base R package.

For computing Spearman correlation coefficients, we used the `cor.test` function from the `stats` package. If there were 3 or fewer data points, then the correlation was not done and a value of `NA` was supplied.

>>>>

- summary paragraph
- study limitations
- future directions

@@
